---
title: "Scopus Articles"
author: "Sanja Miklin"
date: "2/7/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(jsonlite)
library(scales) # optional. can install by running install.packages("scales")
```


```{r read_data}
total_articles <- read.csv("total_articles.csv")
subject_articles <- read.csv("subject_articles.csv")
fields <- read.csv("scopus_subjects.csv")
asjc_codes <- read.csv("asjc.csv")


files <- list.files()
```


# Setting up search parameters

```{r}
key <- "enter your scopus API key here"

year_start <- 1960 #enter year that you wish to start your search
year_end <- 2020 #enter year that you wish to end your search

query <- "TITLE-ABS-KEY ( child AND abuse )" #add your query here

#ignore this last part, it's just defining some other data
url <- "https://api.elsevier.com/content/search/scopus?query="
query <- query %>%
  str_replace_all("\\s", "\\+") %>%
  str_replace_all("\\(", "\\%28") %>%
  str_replace_all("\\)", "\\%29") %>%
  str_replace_all('\\"', '\\%22')
```

The query used to do the search is `r query`, looking at data from `r year_start` to `r year_end`.


# Total number of articles for your topic

NOTE: If running for the first time, make sure to delete "article_count.csv" from the folder.
If that file exists, the code will not run and replace it (this is a failsafe)

```{r total_articles}

if ("article_count.csv" %in% files){
  #read existing file, if any
  article_count <- read.csv("article_count.csv")
} else {
  #create empty data frame
  article_count <- tibble(year = c(year_start:year_end), n=0)

  #run search by year
  for (i in 1:nrow(article_count)){
    year = article_count$year[i]
    call <- paste0(url,"%28+",query,"+AND+PUBYEAR+IS+",year,"+%29&apikey=",key)
    ans <- fromJSON(call)
    article_count$n[i] <- as.integer(ans$`search-results`$`opensearch:totalResults`) 
  }
  
  #join to total scopus counts
  article_count <- article_count%>%
    left_join(total_articles)%>%
    mutate(prop = n/total)
  #save file
  write.csv(article_count, "article_count.csv", row.names = FALSE)
}
```

Plotting articles by year (as total and as proportion of all)

```{r plot_totals}
article_count %>%
  ggplot((aes(x=year, y = n)))+
  geom_line(color="#008080")+
  theme_minimal() +
  labs(title = "Total number of articles on the topic over time")


article_count %>%
  ggplot((aes(x=year, y = prop)))+
  geom_line(color="#008080")+
  theme_minimal()+
  labs(title = "Proportion of all Scopus articles on the topic over time")

```


# Look at changes by subject

NOTE: If running for the first time, make sure to delete "articles_by_subject.csv" from the folder.
If that file exists, the code will not run and replace it (this is a failsafe)

```{r by suject}
if ("articles_by_subject.csv" %in% files){
  #read existing file, if any
  articles_by_subject <- read.csv("articles_by_subject.csv")
} else {
    
  #create empty data frame
  articles_by_subject <- fields %>%
  select(Abb) %>%
  mutate(year = list(year_start:year_end))%>%
  unnest(year)%>%
  mutate(n=0)

  # run search by subject and year
  for (i in 1:nrow(articles_by_subject)){
    year <- articles_by_subject$year[i]
    field <-articles_by_subject$Abb[i]
    call <- paste0(url,"%28+",query,"+AND+SUBJAREA+%28+",field,"+%29+AND+PUBYEAR+IS+",year,"+%29&apikey=",key)
    ans <- fromJSON(call)
    articles_by_subject$n[i] = as.integer(ans$`search-results`$`opensearch:totalResults`) 
  }
  
  #rename columns
  colnames(articles_by_subject) <- c("field", "year", "n")
  
  #combine with total counts
  articles_by_subject <- articles_by_subject %>%
    left_join(subject_articles)%>%
    mutate(prop = n/total)
  
  #save file
  write.csv(articles_by_subject, "articles_by_subject.csv", row.names = FALSE)
}

```



#Find top fields

```{r top_field}

cumulative_subject <- articles_by_subject %>%
  group_by(field)%>%
  summarise(n= sum(n)) %>%
  arrange(-n) %>%
  mutate(total = sum(article_count$n))%>%
  mutate(prop = n/total)

head(cumulative_subject)

```


# Plot changes over times by top fields

```{r plot_by subject}
top_fields <- cumulative_subject[1:4,] #select how many top fields you want to display

articles_by_subject %>%
  filter(field %in% top_fields$field)%>%
  ggplot((aes(x=year, y = prop, color = field)))+
  geom_line()+
  theme_minimal() +
  labs(title = "Proportion of articles in a field on the topic")

articles_by_subject %>%
  filter(field %in% top_fields$field)%>%
  ggplot((aes(x=year, y = prop)))+
  geom_line()+
  theme_minimal()+
  facet_wrap(~field, scales = "free")+
  labs(title = "Proportion of articles in a field on the topic")

```


#if you're interested in specific ASJC code

```{r}

ASJC_list <- c("2735", "3312") # include your ASJC code. if you want to look at more than one code, you should separate them like this c("code1", "code2")

#this code will look for both all articles within a code
#and articles within a code on the particular prolem

if ("articles_by_asjc.csv" %in% files){
  #read existing file, if any
  articles_by_asjc <- read.csv("articles_by_asjc.csv")
} else {
  #create empty df
  articles_by_asjc <- tibble(year = c(year_start:year_end), asjc = list(ASJC_list), total=0, n=0) %>%
    unnest(asjc)
  
  #run search by year
  for (i in 1:nrow(articles_by_asjc)){
    year = articles_by_asjc$year[i]
    asjc = articles_by_asjc$asjc[i]
    
    #look for total articles
    call <- paste0(url,"%28+SUBJTERMS+%28+",asjc,"+%29+AND+PUBYEAR+IS+",year,"+%29&apikey=",key)
    ans <- fromJSON(call)
    articles_by_asjc$total[i] <- as.integer(ans$`search-results`$`opensearch:totalResults`) 
    
    #look for articles on topic
    call <- paste0(url,"%28+",query,"+AND+SUBJTERMS+%28+",asjc,"+%29+AND+PUBYEAR+IS+",year,"+%29&apikey=",key)
    ans <- fromJSON(call)
    articles_by_asjc$n[i] <- as.integer(ans$`search-results`$`opensearch:totalResults`) 
  }
  
  articles_by_asjc <- articles_by_asjc %>%
    mutate(prop = n/total)
  
  write.csv(articles_by_asjc, "articles_by_asjc.csv")

}
```

# plot by ASJC

```{r}

articles_by_asjc %>%
  ggplot((aes(x=year, y = prop, color = asjc)))+
  geom_line()+
  theme_minimal() +
  labs(title = "Proportion of articles in a field on the topic")+
  scale_x_continuous(breaks= pretty_breaks())



articles_by_asjc %>%
  ggplot((aes(x=year, y = prop)))+
  geom_line()+
  theme_minimal()+
  facet_wrap(~asjc, scales = "free")+
  labs(title = "Proportion of articles in a field on the topic")+
  scale_x_continuous(breaks= pretty_breaks())

```

